Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-08 Dissertation/Thesis/tex/ae3Dcomplex.tex
updated from tlee edits, more figs for NRL flight experiment
increased refs from 42 to 61 excluding geometric control ones, which will be added later

In this section, we propose how multiple measurement rays in 3D can determine map information gain from a pose candidate. Then, we show how a collision-free trajectory is determined with a 3D Dijkstra's search. Finally, we combine 3D information gain and travel costs into a single optimization.

@@

>>>>

In this section, we propose how multiple measurement rays in 3D can determine map information gain from a pose candidate~\cite{KauLee19}. Then, we show how a collision-free trajectory is determined with a 3D Dijkstra's search. Finally, we combine 3D information gain and travel costs into a single optimization.

@@

\subsection{Mars Exploration Motivation}

The topography of Mars has several benefits in future mission planning for landing spacecraft and  image distortion correction, among other research objectives. The Mars Orbiting Laser Altimeter (MOLA) mission greatly improved the topography map of the surface, but was limited to an uncertainty of roughly eight meters~\cite{MOLA99}. The only precise topography knowledge about the surface comes from four rovers, two of which are inactive, and have covered only a small portion of the surface area of Mars. Approaches for exploring environments similar to offices, such as \cite{MauDakPet14}, are incompatible with the complex terrain presented in this numerical example.

### 2018-07-08 Dissertation/Thesis/tex/intro.tex
increased refs from 42 to 61 excluding geometric control ones, which will be added later

@@

\paragraph{Learning the Inverse Sensor Model} The approximate nature of the inverse sensor model motivated a solution using machine learning. The main idea is to simulate maps, robot poses, and measurements with simulated noised based on the sensor stochastic properties. Then, an approximation the inverse sensor model is learned using an expectation maximization algorithm~\cite{Thr01,ThrBurFox05}. Unlike approximate functions based on intuition, the machine learning approach is based on the physical properties of sensors. However, this approach is undesirable in practice due to complexities associated to implementing a learning algorithm. For example, the accuracy of such inverse sensor models strongly depends on the samples selected for learning, but it is unclear how to select those samples, or how many samples are required to obtain a reasonable approximation. Furthermore, it is challenging to apply any learning algorithm over the large dimensional space composed of maps, poses, and measurements.

\paragraph{Log-Odds Ratio} Both approaches described above use the log-odds ratio to update grid cell probabilities. The log-odds ratio formulation is a popular framework for updating binary random variables with static state within a Bayesian filter. The main idea is that instead of multiplying terms from prior and current time steps, the properties of logarithms allow these terms to be simply added, while avoiding some truncation issues associated with probabilities close to $0$ or $1$~\cite{ThrBurFox05}. This approach is also popular because the inverse sensor model needs not consider prior probabilities. Instead, these approaches typically consider fixed uniform initial probabilities of all grid cells, which makes the formulation simpler.

@@

The next topic this dissertation addresses is autonomous exploration. The vast majority of work in simultaneous localization and mapping (SLAM) deals only with the aspect of estimating the environment and the poses of vehicles. These approaches are passive in the sense that SLAM is performed on incoming sensor measurements from vehicles following an arbitrary path. As such, human teleoperation and monitoring are often essential to guide the vehicles safely through unknown surroundings. Therefore, it is desirable that an active motion planning scheme is developed and integrated with SLAM such that vehicles are able to determine their path without human intervention, and explore unknown areas autonomously. The two approaches used to solve this problem are described next.

@@

\paragraph{Entropy-Based Autonomous Exploration}
Entropy-based approaches address the suboptimal nature of frontier-based approaches by selecting robotic actions designed to decrease minimize map uncertainty~\cite{StaGriBur05,BurMooStaSch05}. These approaches use a measure of uncertainty known as Shannon's entropy, which becomes smaller as cell probabilities approach $0$ or $1$ (becoming more certain). Existing entropy-based approaches simulate possible future measurements from various locations with so-called ``hallucination measurements,'' which typically corresponds to expected depth measurements from the robot to the closest grid cell that is possibly occupied. Then, the robot analyzes how this measurement would affect the map uncertainty. However, this approach assumes that expected map entropy is equivalent to map entropy from expected measurements. This is not the case in general, however, as there is typically a nonzero probability that the hallucination measurement and true future measurement are not the same. Entropy-based approaches seek to optimize map uncertainty, but require large approximations which can decrease the accuracy of predictions.

>>>>

There are several existing mapping representations including occupancy grids~\cite{WolSuk05,WolSuk05,MeyBeiBur12,TanThoWolBus14}, Octomaps~\cite{WurHorBenStaBur10,HorWurBenStaBur13}, or feature-based maps
~\cite{MonThrKolWeg02}. In this dissertation, we focus on occupancy grid maps because of their simple structure, efficient memory usage, and natural application to autonomous exploration in later sections. Occupancy grid mapping follows a Bayesian framework that focusses on occupied and free space, not tracking particular systems or mapping features, such as visual servoing~\cite{ChiDinChe14}.

@@

\paragraph{Learning the Inverse Sensor Model} The approximate nature of the inverse sensor model motivated a solution using machine learning. The main idea is to simulate maps, robot poses, and measurements with simulated noised based on the sensor stochastic properties. Then, an approximation the inverse sensor model is learned using an expectation maximization algorithm~\cite{Thr01,ThrBurFox05,SouMaiGon12}. Unlike approximate functions based on intuition, the machine learning approach is based on the physical properties of sensors. However, this approach is undesirable in practice due to complexities associated to implementing a learning algorithm. For example, the accuracy of such inverse sensor models strongly depends on the samples selected for learning, but it is unclear how to select those samples, or how many samples are required to obtain a reasonable approximation. Furthermore, it is challenging to apply any learning algorithm over the large dimensional space composed of maps, poses, and measurements.

\paragraph{Log-Odds Ratio} Both approaches described above use the log-odds ratio to update grid cell probabilities. The log-odds ratio formulation is a popular framework for updating binary random variables with static state within a Bayesian filter. The main idea is that instead of multiplying terms from prior and current time steps, the properties of logarithms allow these terms to be simply added, while avoiding some truncation issues associated with probabilities close to $0$ or $1$~\cite{ThrBurFox05,Thr03}. This approach is also popular because the inverse sensor model needs not consider prior probabilities. Instead, these approaches typically consider fixed uniform initial probabilities of all grid cells, which makes the formulation simpler.

@@

The next topic this dissertation addresses is autonomous exploration. The vast majority of work in simultaneous localization and mapping (SLAM) deals only with the aspect of estimating the environment and the poses of vehicles. These approaches are passive in the sense that SLAM is performed on incoming sensor measurements from vehicles following an arbitrary path (e.g.~\cite{ThrBurFox05,DurBai06,CheChe09}). As such, human teleoperation and monitoring are often essential to guide the vehicles safely through unknown surroundings. Therefore, it is desirable that an active motion planning scheme is developed and integrated with SLAM such that vehicles are able to determine their path without human intervention, and explore unknown areas autonomously. The two approaches used to solve this problem are described next.

@@

\paragraph{Entropy-Based Autonomous Exploration}
Entropy-based approaches address the suboptimal nature of frontier-based approaches by selecting robotic actions designed to decrease minimize map uncertainty~\cite{CarDamKumCas15,StaGriBur05,BurMooStaSch05}. These approaches use a measure of uncertainty known as Shannon's entropy, which becomes smaller as cell probabilities approach $0$ or $1$ (becoming more certain). Existing entropy-based approaches simulate possible future measurements from various locations with so-called ``hallucination measurements,'' which typically corresponds to expected depth measurements from the robot to the closest grid cell that is possibly occupied. Then, the robot analyzes how this measurement would affect the map uncertainty. However, this approach assumes that expected map entropy is equivalent to map entropy from expected measurements~\cite{JohStaPfaBur07}. This is not the case in general, however, as there is typically a nonzero probability that the hallucination measurement and true future measurement are not the same. Entropy-based approaches seek to optimize map uncertainty, but require large approximations which can decrease the accuracy of predictions.

### 2018-07-08 Dissertation/Thesis/tex/pogm.tex
increased refs from 42 to 61 excluding geometric control ones, which will be added later

Next, we compare the same approximate inverse sensor model against the synergistic exact inverse sensor model.
Here, the robot maps in a two-dimensional environment composed of ten wall edges, and the robot follows a figure-eight curve, then turns around and completes the same curve in the reverse direction. Like the prior example, the same set of measurements updated each second are used with both occupancy grid mapping algorithms to construct the map.
The resulting maps are illustrated in Figure \ref{fig:NumResOccProbs} for both algorithms, where it is shown that the proposed algorithm yields a substantially more accurate and clear map with less uncertainty.

>>>>

Next, we compare the same approximate inverse sensor model against the synergistic exact inverse sensor model.
Here, the robot maps in a two-dimensional environment composed of ten wall edges, and the robot follows a figure-eight curve, then turns around and completes the same curve in the reverse direction. A pseudo-random measurement scan is sampled at each time step via the inverse transform sampling~\cite{DevBK86}, and like the prior example, the same set of measurements are used with both occupancy grid mapping algorithms to construct the map.
The resulting maps are illustrated in Figure \ref{fig:NumResOccProbs} for both algorithms, where it is shown that the proposed algorithm yields a substantially more accurate and clear map with less uncertainty.
